

\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{titling}

\geometry{a4paper, margin=1in}

\title{Snapshot Objectives}
\author{
    Jasmine Morales\\
    \and Tiana Luu\\
    \and Kira Ma\\
    \and Linda Tien\\
}
\date{December 2025}

\setlength{\droptitle}{6cm}

\pagestyle{fancy}
\fancyhead[L]{Snapshot Objectives}
\fancyhead[R]{Page \thepage}
\fancyfoot[C]{}

\begin{document}

\begin{titlepage}
\maketitle
\thispagestyle{empty}
\end{titlepage}

\section*{Start Objective}
The starting objective of the \textbf{Project Management Web Application} is to establish the core technical foundation and ensure that all team members are aligned on responsibilities. This includes:
\begin{itemize}
    \item Setting up React.js for the frontend to provide a responsive and user-friendly interface.
    \item Implementing Node.js/Express for the backend to handle API requests and server logic.
    \item Configuring MongoDB for persistent data storage of users, tasks, and project information.
    \item Creating a basic UI with login, registration, and navigation to core pages.
    \item Establishing task delegation through Jira to organize the first sprint.
\end{itemize}

\section*{1st Checkpoint Objective}
The primary objective for Snapshot 2 is to implement the first major feature: a project dashboard. This will include:
\begin{itemize}
    \item Data entry and display functionality for tasks and objectives.
    \item Initial synchronization between frontend and backend services.
    \item Integration of TestRail for documenting test cases and results.
    \item Updates to the User Manual and Design Spec to reflect the new dashboard feature.
\end{itemize}

\section*{2nd Checkpoint Objective}
The primary objective for Snapshot 3 is to expand functionality with notifications and reporting. This will include:
\begin{itemize}
    \item Implementing an email or in-app notification system to alert users of task updates.
    \item Adding reporting features to visualize project progress and team performance.
    \item Updating the SDD and SRS documents with new requirements and design changes.
    \item Refining the workflow diagram to reflect expanded system interactions.
\end{itemize}

\section*{Due Date Checkpoint}
The final objective for Snapshot 4 is to polish the application and prepare for submission. This will include:
\begin{itemize}
    \item Fixing bugs and improving UI readability across devices.
    \item Documenting future work, such as advanced analytics or mobile app integration.
    \item Final updates to the User Manual, SDD, and SRS.
    \item Submitting the Snapshot Reflection document and ensuring all deliverables are complete.
\end{itemize}

\end{document}
