\documentclass[12pt]{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{titling}

\geometry{a4paper, margin=1in}

\title{Design Specifications}
\author{
    Jasmine Morales\\
    Tiana Luu\\
    Kira Ma\\
    Linda Tien\\
}
\date{December 2025}

\setlength{\droptitle}{6cm}

\pagestyle{fancy}
\fancyhead[L]{Design Specifications}
\fancyhead[R]{Page \thepage}
\fancyfoot[C]{}

\begin{document}

\begin{titlepage}
\maketitle
\thispagestyle{empty}
\end{titlepage}

\section*{Packages and Dependencies}

\subsection*{Front-End (React.js)}
\begin{itemize}
    \item Node.js (version 18 or higher): JavaScript runtime environment.
    \item npm (version 9 or higher): Package manager.
    \item React.js (react, react-dom, react-scripts): Core frontend framework.
    \item React Router (react-router-dom): For navigation and routing.
    \item Bootstrap / Material UI: For UI components and responsive design.
    \item Axios: For HTTP requests to backend services.
\end{itemize}

\subsection*{Back-End (Node.js/Express)}
\begin{itemize}
    \item Express.js: Web application framework for Node.js.
    \item body-parser: Middleware for handling JSON requests.
    \item cors: Middleware for cross-origin resource sharing.
    \item dotenv: For environment variable management.
    \item jsonwebtoken (JWT): For authentication and authorization.
    \item bcrypt: For password hashing.
    \item multer: For file uploads.
    \item nodemon: For automatic server restarts during development.
\end{itemize}

\subsection*{Database Management (MongoDB)}
\begin{itemize}
    \item MongoDB: NoSQL database for storing project data.
    \item Mongoose: ODM library for interacting with MongoDB.
    \item MongoDB Compass: GUI for database management.
\end{itemize}

\section*{Libraries}
\begin{itemize}
    \item React Router
    \item Axios
    \item Bootstrap / Material UI
    \item bcrypt
    \item jsonwebtoken
    \item multer
    \item nodemon
    \item Mongoose
\end{itemize}

\section*{Deployment and Hosting}
\begin{itemize}
    \item NGINX: Reverse proxy and static file server.
    \item Docker: Containerization of frontend, backend, and database services.
    \item AWS EC2 / Heroku: Cloud hosting options.
\end{itemize}

\end{document}

